CONEM2024-0025\\ ABC MULTICRITERIA CLASSIFICATION WITH ANALYTICAL HIERARCHY PROCESS: HOW TO FORCE CONSISTENCY OF PAIRWISE COMPARISONS MATRIX

### 2024-02-05 accepted/CONEM2024/FCPCOM/CONEM2024.tex
multicriteria ABC classification

@@

\begin{equation}
	\rho_{p} = (wb + wlt) * \frac{b_p}{lt_p} + \sum{w_{\sigma_q}*\frac{b_{e_p}}{lt_{e_p}}} + \sum{w_{\beta_b}*w_{p\beta_b}}
\end{equation}

@@

$\textrm{B}$ is the set of binary criteria, \quad $\textrm{B} = \{\beta_b\}_{b=NQ+1}^{NQ+NB}$;

@@

$e_p$ is the lead time billing equivalent to product $p$;

>>>>

\usepackage{algpseudocode}

@@

\begin{equation}
	\rho_{p} = (wb + wlt) * \frac{b_p}{lt_p} + \sum{w_{\sigma_q}*\frac{b_{e_{p\sigma_q}}}{lt_{e_{p\sigma_q}}}} + \sum{w_{\beta_b}*w_{p\beta_b}}
\end{equation}

@@

$\textrm{B}$ is the set of binary criteria, \quad $\textrm{B} = \{\beta_b\}_{b=1}^{NB}$;

@@

$e_{p\sigma_q}$ is the product lead time billing equivalent to product $p$ on the criterion $\sigma_q$;
